---
title: "HW8_MahimNaveed"
author: "Mahim Naveed"
date: "Sunday, November 09, 2015"
output: html_document
---

From the ggplot2 package, tidy up the "movies" data set. Specifically, variables r1:r10 and Action:Short

```{r cache=TRUE tidy=TRUE}
library(gcookbook); library(ggplot2)
library(dplyr, warn.conflicts=FALSE)
library(broom); library(lubridate); 
library(RCurl); library(tidyr); library(plyr)
library(reshape2)


movies.sorted <- movies %>% 
  select(year, title, r1:r10, Action:Short) %>% 
  gather("rating", "percentage", r1:r10) %>% 
  arrange(year, title) %>% 
  gather("genre", "Logical", Action:Short) %>% 
  filter(Logical==1) %>% 
  select(year, genre, title, rating, percentage)

head(movies.sorted, 25)

View(movies.sorted)

```



From the cafe data set, explain how you would tidy it up. Which variables? "Un-tidy" the data set by the variable Day Code/ Day of Week.

Date can be separated into month and day. 
Day.code and X can be removed as they aren't really needed. 
Columns for sold,wasted and total can be turned into rows, keeping item titles as column names.

```{r cache=TRUE tidy=TRUE}
cafe <- getURL("https://raw.githubusercontent.com/shv38339/statcomp597d/master/data/cafedata.csv")
cafe <- read.csv(file = textConnection(cafe), header = TRUE)

cafe.sorted <- cafe %>%
  select(Date, Day.Code, Day.of.Week, c(5:22)) %>% 
  arrange(Day.Code, Date, Day.of.Week) %>% 
  select(-Day.Code)
  
head(cafe.sorted, 10)
View(cafe.sorted)
```